SafeNet: A European database of plant-pollinator interactions

### 2024-03-01 Manuscript/Figure_2.Rmd
Figure phylo and coverage of bees done!

#Read data
tree_family_interactions= readRDS("../Data/Manuscript_info/bee_phylo.RData")
family_level1 = readRDS("../Data/Manuscript_info/bee_family_info.RData")
bee_plotting = readRDS("../Data/Manuscript_info/bee_plotting.RData")

#Plot
p = ggtree(tree_family_interactions,  size=0.5,  alpha=1)+ 
geom_tippoint(aes(size= Interactions, fill = Pollinator_family), color="black", shape=21) +
geom_tiplab(linetype='dashed', linesize=.05, offset = 0.19, size=2.4, fontface=4) +
labs("log(Species)")+
scale_size(name = "Species", range = c(0, 5.5)) +
guides(fill = "none") +
theme(legend.position = "bottom")

p1 = p + 
new_scale_fill() +
geom_fruit(data=family_level1, geom=geom_bar,
      mapping=aes(y=Pollinator_genus, x=Interactions1, 
      fill = Pollinator_family1),
      pwidth=0.19, 
      orientation="y", 
      stat="identity",
      color="black",
      offset = 0.23,
      axis.params=list(axis       = "x",
                         text.size= 1.8,
                         hjust    = 1,
                         vjust      = 0.5,
                         nbreak     = 2),grid.params=list())  +
theme(legend.position = "bottom")

p2 = ggplot(data = bee_plotting, aes(reorder(Pollinator_family, -Spp_number), 
       Spp_number, fill = Group, pattern = Group)) +
geom_col_pattern(position = "dodge",color = "black", pattern_fill = "black") +
scale_pattern_manual(values = c(A = "stripe", B = "none"), labels= c(A = "SafeNet spp", B = "European spp")) +
scale_fill_manual(values = c(A = "tan2", B = "black"), labels= c(A = "SafeNet spp", B = "European spp")) + 
coord_cartesian(expand = FALSE) +
theme_bw() + 
ylab("Number of species") +
xlab("")+
ggtitle("Bee family coverage") +
theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1, face = "bold"),
 legend.box.margin=margin(40,40,40,40),
 legend.position = "bottom")

p2_1 = plot_grid(NULL,p2,NULL, ncol = 1, rel_heights  = c(1, 1.5, 0.5),rel_widths  = c(0.1, 2, 0.1))
plot_grid(p1,p2_1, rel_widths = c(2, 2), rel_heights  = c(4, 0.4), align = "none")

>>>>

#Read data
tree_family_interactions= readRDS("../Data/Manuscript_info/bee_phylo.RData")
d1 = readRDS("../Data/Manuscript_info/bee_data.RData")
n = readRDS("../Data/Manuscript_info/node_data.RData")

#Circular layour
ggtree(tree_family_interactions, size=0.6, open.angle=1, alpha=1)+ 
geom_tippoint(aes(size= Interactions), fill = "tan2", color="black", shape=21) +
geom_tiplab(linetype='dashed', linesize=.05, offset = 0.062, size=2.5, fontface=1) +
scale_size(name = "Log(Interactions)", range = c(0,4.5))  +
theme(legend.position = "bottom") +
new_scale_fill() +
geom_fruit(data = d1, geom=geom_bar,
                    mapping=aes(y=Genus1, x=Percent, fill = fam_group),
                    pwidth=0.1, 
                    orientation="y", 
                    stat="identity",
                    color="black",
                    offset = 0.128,
            axis.params=list(
                         axis = "x",
                         text.size  = 2.5,
                         hjust  = 1,
                         vjust = 0.5,
                         nbreak = 3,
                         fontface = 2
                     ),
         grid.params=list()) +
guides(fill = "none")+
scale_fill_manual(values = c(a = "tan2", b = "lightblue3"), guide = "none")+
geom_fruit(geom=geom_bar,
                    mapping=aes(y=label, x=Spp_number_Europe),
                    pwidth=0.1, 
                    orientation="y", 
                    stat="identity",
                    color="black",
                    offset = 0,
            axis.params=list(
                         axis = "x",
                         text.size  = 2.5,
                         hjust  = 1,
                         vjust = 0.5,
                         nbreak = 1,
                         fontface = 2
                     ),
         grid.params=list()) +
annotate("text", x = 14, y = 70, label = "SafeNet spp\n coverage (%)", size= 2.65, fontface= "bold") +
annotate("text", x = 15.2, y = 70, label = "European\n species", size= 2.65, fontface= "bold")+
annotate("text", x = 12.1, y = 70, label = "SafeNet\n interactions", size= 2.65, fontface= "bold")+ 
new_scale_fill() +
geom_hilight(data=n, aes(node=node), type = "roundrect", fill = "orange") +
annotate("text", x = 7.5, y = 2.8, label = "Melittidae", size= 3)+
annotate("text", x = 7, y = 6.5, label = "Andrenidae", size= 3)+
annotate("text", x = 9.5, y = 12.5, label = "Colletidae", size= 3)+
annotate("text", x = 5.9, y = 17.4, label = "Halictidae", size= 3)+
annotate("text", x = 2.8, y = 28.6, label = "Apidae", size= 3)+
annotate("text", x = 2.8, y = 51.3, label = "Megachilidae", size= 3) +
coord_cartesian(clip = "off")+
theme(legend.margin=unit(1,"cm"),
      legend.spacing = unit(1, "cm"),
      plot.margin = margin(4,0,4,0), 
      legend.position = c(0.6,0),
      legend.direction = "horizontal")

### 2024-03-01 Manuscript/Ms.qmd
Figure phylo and coverage of bees done!

FIGURE 3 POLLINATOR COVERAGE

>>>>

```{r echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE, out.width="95%", fig.width=10, fig.height=10, fig.cap= "\\textbf{Figure 2}. Phylogenetic representation of the bee genera in the SafeNet database within the context of all European bee genera. The number of interactions recorded in the database per genus is depicted with circles of proportional size corresponding to the number of interactions. The coverage of species per genus is depicted with orange and light blue bars, representing the percentage of species included and not included in the database, respectively, out of the total number of species per genus at the European level. Grey bars indicate the total number of species per genus at the European level."}

#Load libraries
library(ggplot2)
library(ggnewscale)
library(ggtreeExtra)
library(ggtree)
library(ggpattern)
library(patchwork)
library(cowplot)

#Read data
tree_family_interactions= readRDS("../Data/Manuscript_info/bee_phylo.RData")
d1 = readRDS("../Data/Manuscript_info/bee_data.RData")
n = readRDS("../Data/Manuscript_info/node_data.RData")

#Circular layour
ggtree(tree_family_interactions, size=0.6, open.angle=1, alpha=1)+ 
geom_tippoint(aes(size= Interactions), fill = "tan2", color="black", shape=21) +
geom_tiplab(linetype='dashed', linesize=.05, offset = 0.063, size=2.9, fontface=1) +
scale_size(name = "Log(Interactions)", range = c(0,4.5))  +
theme(legend.position = "bottom") +
new_scale_fill() +
geom_fruit(data = d1, geom=geom_bar,
                    mapping=aes(y=Genus1, x=Percent, fill = fam_group),
                    pwidth=0.12, 
                    orientation="y", 
                    stat="identity",
                    color="black",
                    offset = 0.137,
            axis.params=list(
                         axis = "x",
                         text.size  = 2.5,
                         hjust  = 1,
                         vjust = 0.5,
                         nbreak = 3,
                         fontface = 2
                     ),
         grid.params=list()) +
guides(fill = "none")+
scale_fill_manual(values = c(a = "tan2", b = "lightblue3"), guide = "none")+
geom_fruit(geom=geom_bar,
                    mapping=aes(y=label, x=Spp_number_Europe),
                    pwidth=0.12, 
                    orientation="y", 
                    stat="identity",
                    color="black",
                    offset = 0,
            axis.params=list(
                         axis = "x",
                         text.size  = 2.5,
                         hjust  = 1,
                         vjust = 0.5,
                         nbreak = 1,
                         fontface = 2
                     ),
         grid.params=list()) +
annotate("text", x = 14.2, y = 70, label = "SafeNet spp\n coverage (%)", size= 3, fontface= "bold") +
annotate("text", x = 15.7, y = 70, label = "European\n species", size= 3, fontface= "bold")+
annotate("text", x = 12.1, y = 70, label = "SafeNet\n interactions", size= 3, fontface= "bold")+ 
new_scale_fill() +
geom_hilight(data=n, aes(node=node), type = "roundrect", fill = "orange") +
annotate("text", x = 7.5, y = 2.8, label = "Melittidae", size= 3)+
annotate("text", x = 7, y = 6.5, label = "Andrenidae", size= 3)+
annotate("text", x = 9.5, y = 12.5, label = "Colletidae", size= 3)+
annotate("text", x = 5.9, y = 17.4, label = "Halictidae", size= 3)+
annotate("text", x = 2.8, y = 28.6, label = "Apidae", size= 3)+
annotate("text", x = 2.8, y = 51.3, label = "Megachilidae", size= 3) +
coord_cartesian(clip = "off")+
theme(legend.margin=unit(1,"cm"),
      legend.spacing = unit(1, "cm"),
      plot.margin = margin(4,0,4,0), 
      legend.position = c(0.6,0),
      legend.direction = "horizontal")
